STAT 3494W Proposal

### 2022-10-10 Proposal/proposal.tex
edit intro

\section*{Introduction}
\label{sec:intro}
I will be researching the effects of the Covid-19 pandemic on influenza vaccination rates within the United States. This topic
is important because research has shown that "Vaccinated patients testing positive for COVID-19 were less likely to require hospitalization 
(odds ratio, 0.58, 95\% CI 0.46-0.73; $P< .001$), or mechanical ventilation (odds ratio, 0.45, 95\% CI 0.27-0.78; P = .004) and had a shorter 
hospital length of stay (risk ratio, 0.76, 95\% CI 0.65-0.89; $P< .001$)" \citep{conlon2021impact}. Thus, by determining if there are decreases
in vaccination rates, medical and public health professionals may be able to implement strategies for increasing the rate, so that there is less 
severity in covid infections.

@@

\section*{Conclustion}
\label{sec:Conclusion}
Research has shown that recieving the influenza vaccine may be associated with less severe covid-19 cases. Thus, it is important to have high influenza vaccination
rates, but this is only possible if there is equal acccess to health care among all racial groups regardless of socioeconomic status. Currently, this is not the case
within the United States. By studying how the influenza vaccination rates have changed before, during, and after the pandemic among different age groups, race, and
healthcare versus non-healthcare workers, I hope to have a better understanding of how each group has been effected by the pandemic. If there are dispareties among the 
racial groups, this information can be used among researchers to implement new polices or strategies, so that these groups can have equal access to the vaccine.

>>>>

\section*{Introduction}
\label{sec:intro}
I will be researching the effects of the Covid-19 pandemic on influenza vaccination rates within the United States. This topic
is important because research has shown that "Vaccinated patients testing positive for COVID-19 were less likely to require hospitalization 
(odds ratio, 0.58, 95\% CI 0.46-0.73; $P< .001$), or mechanical ventilation (odds ratio, 0.45, 95\% CI 0.27-0.78; P = .004) and had a shorter 
hospital length of stay (risk ratio, 0.76, 95\% CI 0.65-0.89; $P< .001$)" \citep{conlon2021impact}. Thus, by determining if there are decreases
in vaccination rates, medical and public health professionals may be able to implement strategies for increasing the rate, so that there is less 
severity in covid infections. However, there has only been one study that has calulated the difference in influenza vaccination proportions prior 
to and after the pandemic and it only focuses on a state level \citep{leuchter2022association}. Other studies focus on how the attitudes towards
recieving the vaccine have changed, if the COVID-19 pandemic was an incentive for the influenza vaccine, and how the pandemic has shifted parents' 
intentions to vaccinated their children. As a result, I would like to analyze the proportions on an age and race basis to determine if there are 
any discrepancies.

@@

\section*{Conclustion}
\label{sec:Conclusion}
Research has shown that recieving the influenza vaccine may be associated with less severe covid-19 cases. Thus, it is important to have high influenza vaccination
rates, but this is only possible if there is equal acccess to health care among all racial groups regardless of socioeconomic status. Currently, this is not the case
within the United States. By studying how the influenza vaccination rates have changed before, during, and after the pandemic among different age groups, race, and
healthcare versus non-healthcare workers, I hope to have a better understanding of how each group has been effected by the pandemic. If there are discrepancies among the 
racial groups, this information can be used among researchers to implement new polices or strategies, so that these groups can have equal access to the vaccine.
